---
title: "Epi Group admin"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sdcar)
```

This document details the uses of this package for managing the main
activities Steno Aarhus Epidemiology Group. Presently, there are two
main tasks for managing the group:

-   Maintaining the calendar that people subscribe to in order to be
    informed about upcoming events. This mainly includes adding new
    events to the existing calendar.
-   Adding upcoming events to the Epi group's GitHub Project Board as
    GitHub Issues.

## Maintaining the calendar

Right now, we have one calendar that we use to inform people about the
regular sessions we hold. This calendar is stored on the sdcar's GitHub
repo as an `.ics` iCal file, which people can use to subscribe to so
that they keep updated on these sessions.

To get the calendar details, use:

```{r}
current_sessions <- epi_get_calendar(epi_calendar_url)
current_sessions
```

To add events to the calendar, you need to create a datetime character
vector of the upcoming dates and their starting time. Because working
with dates can be tricky, we recommend using the
`lubridate::as_datetime()` function for this, along with explicitly
setting the timezone:

```{r}
upcoming_sessions <- lubridate::as_datetime(c(
  "2024-01-06 13:00:00",
  "2024-02-03 13:00:00",
  "2024-03-03 13:00:00",
  "2024-03-31 13:00:00",
  "2024-05-05 13:00:00",
  "2024-06-02 13:00:00",
  "2024-09-01 13:00:00",
  "2024-10-06 13:00:00",
  "2024-11-03 13:00:00",
  "2024-12-01 13:00:00"
), tz = "Europe/Copenhagen")
upcoming_sessions
```

Then use this function to add the events to the calendar (without
updating the calendar file just yet). Since all the regular sessions are
by default 2 hours, we can add two hours to the end date of the upcoming
dates and it gives the end time for the sessions.

```{r}
upcoming_events <- epi_create_sessions(
  start = upcoming_sessions,
  end = upcoming_sessions + lubridate::hours(2)
)
```

If you want to create an event that isn't the regular sessions, use:

```{r}
conference_event <- cal_create_event(
  start = lubridate::now(),
  end = lubridate::now() + lubridate::hours(1),
  title = "Conference",
  description = "Cool conference!"
)

current_sessions |>
  epi_add_sessions(conference_event)
```

Once these dates are created, we need to add them to the existing
calendar. While you could overwrite the existing calendar with these new
dates, it is nice to have a record of all the past sessions in the
calendar. So what we need to do is join the current calendar with these
new events.

```{r}
updated_calendar <- current_sessions |>
  epi_add_sessions(upcoming_events)
```

To save this back to a file, we'll use the `write_ical()` function:

```{r, eval=FALSE}
updated_calendar |>
  write_ical("inst/epi-calendar.ics")
```

## Maintaining the GitHub Project Board

The second task is to add the upcoming sessions to the GitHub Project.
Thankfully, it is a bit easier to do than updating the calendar.

```{r, eval=FALSE}
# Hasn't been fully implemented yet.
upcoming_sessions |>
  epi_create_session_issues()
```
